%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template for Cover Letter
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Authors:
% Claud D. Park <posquit0.bj@gmail.com>
% Lars Richter <mail@ayeks.de>
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%


%-------------------------------------------------------------------------------
% CONFIGURATIONS
%-------------------------------------------------------------------------------
% A4 paper size by default, use 'letterpaper' for US letter
\documentclass[11pt, a4paper]{awesome-cv}

% Configure page margins with geometry
\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}

% Color for highlights
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight
\colorlet{awesome}{awesome-orange}
% Uncomment if you would like to specify your own color
% \definecolor{awesome}{HTML}{CA63A8}

% Colors for text
% Uncomment if you would like to specify your own color
% \definecolor{darktext}{HTML}{414141}
% \definecolor{text}{HTML}{333333}
% \definecolor{graytext}{HTML}{5D5D5D}
% \definecolor{lighttext}{HTML}{999999}
% \definecolor{sectiondivider}{HTML}{5D5D5D}

% Set false if you don't want to highlight section with awesome color
\setbool{acvSectionColorHighlight}{true}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}


%-------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%-------------------------------------------------------------------------------
% Available options: circle|rectangle,edge/noedge,left/right
%\photo[circle,noedge,left]{./examples/profile}
\name{Dr. Ian C.}{Weaver}
\position{Education{\enskip\cdotp\enskip}Software{\enskip\cdotp\enskip}Outreach}
\address{San Francisco, CA, USA}

\mobile{(+1) 202 643 3163}
\email{weaveric@gmail.com}
%\dateofbirth{January 1st, 1970}
\homepage{icweaver.github.io}
\github{icweaver}
\linkedin{icweaver}
% \gitlab{gitlab-id}
% \stackoverflow{SO-id}{SO-name}
% \twitter{@twit}
% \skype{skype-id}
% \reddit{reddit-id}
% \medium{madium-id}
% \kaggle{kaggle-id}
% \googlescholar{googlescholar-id}{name-to-display}
%% \firstname and \lastname will be used
% \googlescholar{googlescholar-id}{}
% \extrainfo{extra information}

%quote{``Be the change that you want to see in the world."}


%-------------------------------------------------------------------------------
%	LETTER INFORMATION
%	All of the below lines must be filled out
%-------------------------------------------------------------------------------
% The company being applied to
\recipient
  {SETI Institute Affiliates program}
  {Mountain View, CA, US}
% The date on the letter, default is the date of compilation
\letterdate{\today}
% The title of the letter
\lettertitle{Application for SETI Affiliate position}
% How the letter is opened
\letteropening{Dear all,}
% How the letter is closed
\letterclosing{Sincerely,}
% Any enclosures with the letter
\letterenclosure[Attached]{Curriculum Vitae}


%-------------------------------------------------------------------------------
\begin{document}

% Print the header with above personal information
% Give optional argument to change alignment(C: center, L: left, R: right)
\makecvheader[R]

% Print the footer with 3 arguments(<left>, <center>, <right>)
% Leave any of these blank if they are not needed
\makecvfooter
  {\today}
  {Dr. Ian C. Weaver~~~·~~~Cover Letter}
  {}

% Print the title with above letter information
\makelettertitle

%-------------------------------------------------------------------------------
%	LETTER CONTENT
%-------------------------------------------------------------------------------
\begin{cvletter}
I am writing to express my sincere interest in the opportunity to be a SETI Institute Affiliate.

During my time as an undergraduate student at UC Santa Cruz, I had the privilege to provide
teaching and mentorship support for the introductory physics courses as part of the nationally
recognized academic support program, the Academic Excellence Program (ACE), which is
dedicated to increasing the diversity of students in STEM. Some of my favorite memories from this
experience involved the pauses where I would take a step back from the chalkboard/whiteboard
and watch as my students would collaborate with each other in smaller groups and even pull up
their own board to brainstorm over the day's learning objectives together. During my three years
with this program, I learned invaluable lessons and tools for being an effective teacher in a
classroom setting, and I applied these active-learning principles to my teaching duties as a
graduate student.

Last year, I graduated with my doctorate in Astronomy \& Astrophysics from Harvard
University. In addition to conducting my own research on the characterization of the atmospheres
of an under-studied population of exoplanets known as high-gravity hot Jupiters as part of an
international collaboration, I had the chance to participate in several teaching and mentorship
opportunities. These included i) providing teaching support and office hours for three separate
undergraduate lower and upper division courses, ii) participating in the intensive teaching training
program, the Institute for Scientist and Engineer Educators Professional Development Program
(ISEE PDP), to develop and teach a week long summer workshop in stellar evolution for the
Banneker Institute, a college preparation program for historically marginalized students in STEM,
and iii) creating a science outreach chapter at my school, Open Labs at Harvard (OLAH), dedicated
to providing educational programs to the greater Boston area by combining bite-sized TED talk
inspired presentations geared towards a general audience with active group engagement.

I am passionate about providing folks with the tools they need to not only tackle the problems
before them, but to also develop their own inquiry based intuition that they can apply to their own future work. I personally see this SETI Affiliate position as an exciting
opportunity for me to apply the tools I have gathered during my time as an undergraduate and
graduate student researcher, teacher, and mentor to make a positive impact on a growing population of citizen scientists, and to promote a diverse, equitable, and inclusive environment. Thank
you in advance for your consideration, and I look forward to hearing from you at your earliest
convenience!
\end{cvletter}


%-------------------------------------------------------------------------------
% Print the signature and enclosures with above letter information
\makeletterclosing

\end{document}
