\cvsection{Work Experience}

\begin{cventries}

  \cventry
    {Onaketa and AJ Tutoring} % Organization
    {Private Tutor} % Job title
    {2022 May - Present} % Date(s)
    {San Francisco, CA} % Location
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item Coordinate tutor-student matching, provide administrative support, and contribute to growth \& brand development.
        \item Provide in-person tutoring for high school physics and math courses \href{https://www.ajtutoring.com/meet-our-team/ian-weaver/}{[AJ Tutoring]}, and online tutoring/mentorship for high school students from underrepresented backgrounds in STEM \href{https://www.onaketa.org/about}{[onaketa.org]}.
        \item Create custom study materials for students and communicated learning outcomes and progress reports to parents/guardians.
      \end{cvitems}
    }
  
  \cventry
    {The Center for Astrophysics | Harvard \& Smithsonian (CfA)} % Organization
    {Graduate Student Researcher} % Job title
    {2016 Sep - 2022 May} % Date(s)
    {Cambridge, MA} % Location
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item Provided spectroscopic time-series observations and follow-up atmospheric analysis for an underrepresented class of exoplanet.
        \item Accomplished this using Gaussian process (GP) and principal component analysis (PCA) detrending techniques, combined with Bayesian inference frameworks including Markov chain Monte Carlo (MCMC) and nested sampling.
        \item Utilized high performance computing facilities and schedulers (Torque/PBS, SGE, slurm) via ssh and the command line on different Linux operating systems.
        \item Taught/mentored several undergraduate courses in Astronomy and received multiple teaching awards.
        \item Operated and maintained the 0.4 meter Clay Telescope atop the Harvard University Science Center.
        \item Hosted star parties and other outreach events for the undergraduate and local community.
      \end{cvitems}
    }
    
  \cventry
    {Banneker Institute } % Organization
    {Course Instructor} % Job title
    {2017 Jun - 2019 Sep} % Date(s)
    {Cambridge, MA} % Location
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item Collaborated in the design and execution of a novel summer astronomy workshop through the ISEE Professional Development Program geared towards underrepresented students in STEM.
        \item Taught 20+ class size emphasizing hands-on and inquiry based learning.undergraduate and local community.
      \end{cvitems}
    }

\end{cventries}
