\cvsection{Work Experience}

\begin{cventries}

  \cventry
    {
    SETI - Unistellar \href{https://www.seti.org/unistellar-college-astronomy-network-ucan}{[link]}
    }
    {Astronomer and Education Program Lead}
    {2023 Aug - Present}
    {San Francisco, CA}
    {
      \begin{cvitems}
        \item Director of UCAN program, providing free telescopes and educational material to community colleges nationwide.
        \item Host star parties in national parks to increase public engagement in astronomy.
      \end{cvitems}
    }

  \cventry
    {Onaketa} % Organization
    {Tutor Coordinator and Administrative Assistant} % Job title
    {2022 May - Present} % Date(s)
    {Oakland, CA} % Location
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item Coordinate tutor-student matching, provide administrative support, and contribute to growth \& brand development.
        \item Provide free online tutoring and mentoring support for high school students from underrepresented backgrounds in STEM \href{https://www.onaketa.org/about}{[onaketa.org]}.
        \item Create custom study materials for students and communicated learning outcomes and progress reports to parents/guardians.
      \end{cvitems}
    }
  
  \cventry
    {The Center for Astrophysics | Harvard \& Smithsonian (CfA)} % Organization
    {Graduate Student Researcher} % Job title
    {2016 Sep - 2022 May} % Date(s)
    {Cambridge, MA} % Location
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item Provided spectroscopic time-series observations and follow-up atmospheric analysis for an underrepresented class of exoplanet.
        \item Utilized high performance computing facilities and schedulers (Torque/PBS, SGE, slurm) via ssh and the command line on different Linux operating systems.
        \item Taught/mentored several undergraduate courses in Astronomy and received multiple teaching awards.
        \item Operated and maintained the 0.4 meter Clay Telescope atop the Harvard University Science Center.
      \end{cvitems}
    }
    
  \cventry
    {Banneker Institute } % Organization
    {Course Instructor} % Job title
    {2017 Jun - 2019 Sep} % Date(s)
    {Cambridge, MA} % Location
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item Collaborated in the design and execution of a novel summer astronomy workshop through the ISEE Professional Development Program geared towards underrepresented students in STEM.
        \item Taught 20+ class size emphasizing hands-on and inquiry based learning.undergraduate and local community.
      \end{cvitems}
    }

\end{cventries}
